Finite Property Convex Elicitation Paper

### 2019-01-28 cvx-fin.tex
Added todo in the appendix

\section{Considering unlabeled properties}
\begin{lemma}\label{lem:trim-full-dim}
  Consider a nondegenerate, elicitable property $\Gamma$ with finitely many level sets.
  Every $\theta \in \Theta := \trim(\Gamma)$ is maximal.  
\end{lemma}
\begin{proof}
  Consider an arbitrary level set $\theta$.
  If $\theta$ is not maximal, then it must be the intersection of some maximal level sets in $\trim(\Gamma)$.
  Therefore, it is a proper subset of the level sets of which it is the intersection, and so it is not in the $\trim$ as it is in the subtracted set.
\end{proof}

>>>>

\section{Considering unlabeled properties}
\begin{lemma}\label{lem:trim-full-dim}
  Consider a nondegenerate, elicitable property $\Gamma$ with finitely many level sets.
  Every $\theta \in \Theta := \trim(\Gamma)$ is maximal.  
\end{lemma}
\begin{proof}
  Consider an arbitrary level set $\theta$.
  If $\theta$ is not maximal, then it must be the intersection of some maximal level sets in $\trim(\Gamma)$.\jessiet{Why?  Add more details about why the level set can't span two maximal level sets}
  Therefore, it is a proper subset of the level sets of which it is the intersection, and so it is not in the $\trim$ as it is in the subtracted set.
\end{proof}
